Bayesian Shape Reconstruction and Optimal Guidance for Autonomous Landing on Asteroids

### 2019-02-03 manuscript.tex
Add translational control

\todo{Augment dynamic model with the control force and the torque}

@@

We utilize a geometric tracking control system to follow the desired trajectory for the position and the attitude defined above.

\todo{add description of control}

>>>>

@@

We utilize a geometric tracking control system to follow the desired trajectory for the position and the attitude defined above. 
The spacecraft is assumed to be fully controllable and as a result the translational and rotational dynamics can be decoupled.
We first derive a translational controller to track an arbitrary position and velocity followed by an attitude controller.

The required translational control are defined in terms of the position and velocity tracking errors.
The tracking error vectors are easier to define as they evolve on a Euclidean space rather than a nonlinear manifold and are given by
\begin{subequations}\label{eq:translation_error_variables}
\begin{align}
    e_x &= x - x_d ,\\
    e_v &= v - \dot{x}_d.
\end{align}
\end{subequations}
The error dynamics are given by
\begin{subequations}\label{eq:translation_error_dynamics}
\begin{align}
    \dot{e}_x &= v - \dot{x}_d, \\
    \dot{e}_v &= \dot{v} - \ddot{x}_d .
\end{align}
\end{subequations}
A control input, \( u_f \), is derived to ensure asymptotic trajectory tracking for the translational dynamics.
\begin{prop}[Control for Translation Dynamics]\label{prop:translational_control}
    Given a desired trajectory \( \vc{x}_d \) and positive constants \( k_x, k_v, c \in \R \) we define a control input \( \vc{u}_f \in \R \) as follows:
    \begin{align}\label{eq:translational_control}
        \vc{u}_f = -k_x e_x - k_v e_v - F_{ext} + m \ddot{x}_d .
    \end{align}
    If \( c \) is chosen such that
    \begin{align}\label{eq:translational_control_gain_bound}
        0 < c < \min \braces{\sqrt{k_x m}, \frac{4 k_x k_v m}{ k_v \parenth{4 k_x m - k_v} }   }
    \end{align}
    then the zero equilibrium of the error vectors~\cref{eq:translation_error_variables} is stable in the sense of Lyapunov.
    Furthermore, \( e_x, e_v \to 0 \) as \( t \to \infty\).
\end{prop}
\begin{proof}
The translational dynamics can be defined as
\begin{align}\label{eq:translation_dynamics_simple}
    \dot{x} &= v , \\
    m \dot{v} &= F_{ext} + u_f ,
\end{align}
where \( m \in \R \) is defined as the total mass of the vehicle while \( F_{ext} \) is the total external force.

Consider the Lyapunov function
\begin{align}\label{eq:translational_lyapunov}
    V = \frac{1}{2} k_x e_x^T e_x + \frac{1}{2} m e_v^T e_v + c e_x^T e_x.
\end{align}
\Cref{eq:translational_lyapunov} is also equivalent to
\begin{align}\label{eq:translational_lyapunov_matrix}
    V = z^T W_1 z , 
\end{align}
where \( z = \begin{bmatrix} \norm{e_x} & \norm{e_v} \end{bmatrix}^T \) and \( W_1\in \R^2\) is defined as
\begin{align}\label{eq:translational_lyapunov_W}
    W_1 = \begin{bmatrix}
        \frac{1}{2} k_x & \frac{1}{2} c \\
        \frac{1}{2} c & \frac{1}{2} m 
    \end{bmatrix}.
\end{align}
The time derivative of~\cref{eq:translational_lyapunov} can then be defined as
\begin{align}\label{eq:translation_lyapunov_derivative}
    \dot{\mathcal{V} } = - \parenth{k_v - c} e_v^T e_v - \frac{k_x c}{m} e_x^T e_x - \frac{k_v c}{m} e_x^T e_v, 
\end{align}
where we used~\cref{eq:translational_control,eq:translation_error_variables,eq:translation_error_dynamics}.
\Cref{eq:translation_lyapunov_derivative} can also be redefined as
\begin{align}\label{eq:translational_lyapunov_derivative_matrix}
    \dot{\mathcal{V}} = - z^T W_2 z, 
\end{align}
where \( W_2 \in \R^2 \) is defined as
\begin{align}\label{eq:translational_lyapunov_W2}
    W_2 = \begin{bmatrix}
        \frac{k_x c}{m} & \frac{k_v^2 c^2}{2 m^2} \\
        \frac{k_v c}{2 m} & k_v - c
    \end{bmatrix}.
\end{align}
If \( c \) is chosen such that~\cref{eq:translational_control_gain_bound} is satisfied then \( W_1, W_2 \) will be positive definite.
As a result, this shows that \( \mathcal{V} > 0 , \dot{ \mathcal{V}} < 0 \) and that the zero equilibrium of the error variables, namely \( x_d, \dot{x}_d \) is asymptotically stable~\cite{khalil1996}.
\end{proof}

The control gains are chosen based on the desired closed-loop system response. 
A variety of techniques are available to choose these gains, but a simple linear analysis offers a straightforward and systematic approach to choosing suitable values. 
We use the control inputs defined in~\cref{eq:translational_control,eqn:adaptive_control} and substitute them into the dynamic equations of motion in~\cref{eq:inertial_position_dynamics,eq:inertial_velocity_dynamics,eq:inertial_attitude_dynamics,eq:inertial_angvel_dynamics}.
\todo{add description of control}
